---
title: "Untitled"
output: github_document
---

Start
```{r}
require(ade4)

 train.data <- read.table("data/sylva_train.data")
 train.labels <- read.table("data/sylva_train.labels")
 train.labels$V1 <- as.factor(train.labels$V1)
 colnames(train.labels)[1] <- "Y"
 train.full=(cbind(train.labels,train.data))
 table(train.labels)
 acp.train <- princomp(train.data, center = TRUE,scale. = TRUE)
 sdd<-acp.train$sdev
 t(acp.train$sdev[acp.train$sdev>=1])
 print (acp.train)
 plot( acp.train , type = "l")
 plot(1-cumsum(acp.train$sdev^2 / sum(acp.train$sdev^2)))
 print(1-cumsum(acp.train$sdev^2 / sum(acp.train$sdev^2))) 
 #statistiques descriptives
summary(train.data)
train.quali<-train.data[,c(1,2,4:6,8,9,11:17,19:40,44:49,51:54,56:74,77:80,82:87,90:99,101:103,106:109,111,112,114:116,118:124,128:138,140:142,144:146,148,149,151:154,156:165,167:170,172:178,180,181,184:186,189,190,192:200,202:204,206,207,209,210,212:216)]
train.quant<-train.data[,c(3,7,10,18,41,42,43,50,55,75,76,81,88,89,100,104,105,110,113,117,125,126,127,139,143,147,150,155,166,171,179,182,183,187,188,191,201,205,208,211)]
ncol(train.quali)+ncol(train.quant)
ncol(train.data)
for(i in 1:ncol(train.quali)){
    train.quali[,i]=as.factor(train.quali[,i])
}
train.qualAcm<-dudi.acm(train.quali,nf=ncol(train.quali),scannf = FALSE)
burtd<-acm.burt(train.quali,train.quali)
image(data.matrix(burtd))
levelplot(data.matrix(burtd),aspect="iso",pretty=TRUE,xlim=c(1,199), ylim=c(1,199))
train.qualAcm$cr

library(FactoMineR)
mca<-MCA(train.quali,ncp=ncol(train.quali))
train.qualAcm<-mca$ind$coord
print(mca)
summary(mca)
#dessine correlation
corMAt<-cor(train.quant)
image(corMAt)
library(lattice)
levelplot(corMAt,aspect="iso",pretty=TRUE,xlim=c(1,ncol(train.quant)), ylim=c(1,ncol(train.quant)))

graphics.off()
par(mfrow=c(4,5))
nb<-ncol(train.data)
for (i in 1:nb){
  hist(train.data[,i],main = paste("Variable",i))

}

#mat
train.quantRed<-scale(train.quant,center = TRUE,scale = TRUE)[,1]

train.quantQual<-cbind(train.quantRed,train.qualAcm)
train.full<-(cbind(train.labels,train.quantQual,train.qualAcm))

res.pca = PCA(train.quantQual, scale.unit=FALSE, ncp=ncol(train.quantQual), graph=T)
res.pca$eig

library(randomForest)
iris.rf <- randomForest(Y ~ ., data=train.full, importance=TRUE,proximity=TRUE)
plot(iris.rf, log="y")
varImpPlot(iris.rf)
MDSplot(iris.rf, train.full$Y)
iris.p <- classCenter(train, labels, iris.rf$prox)
plot(iris[,3], iris[,4], pch=21, xlab=names(iris)[3], ylab=names(iris)[4],
bg=c("red", "blue", "green")[as.numeric(factor(iris$Species))],
main="Iris Data with Prototypes")
points(iris.p[,3], iris.p[,4], pch=21, cex=2, bg=c("red", "blue", "green"))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
