---
title: "Untitled"
output: github_document
---

Start
```{r}
 train = read.table("data/sylva_train.data")
 labels = read.table("data/sylva_train.labels")
 table(labels)
 acp.train <- princomp(train, cor = T, scores = T)
 
 #statistiques descriptives
summary(train)
cor(train)
#nuages de points.
png("p3_sa_para.png", 4096, 4096)
pairs(train)
dev.off()

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
